---
title: "Bank Marketing Campaign Analysis"
author: "Gulnar Hasanova"
date: "`r Sys.Date()`"
output: html_document
---

## Executive Summary
> This report analyzes the efficiency of a Portuguese bank's direct marketing campaign. Using statistical tests and logistic regression, we identify the key factors that drive customers to subscribe to a term deposit.

```{r setup, include=TRUE,echo=TRUE,warning=FALSE,message=FALSE,error=FALSE}
library(ggplot2)
library(dplyr)
df <- read.csv("bank-full.csv", sep = ";", stringsAsFactors = TRUE)
```


## 1. Distribution of Target Variable
> We first analyze how many customers subscribed to the term deposit.

```{r 1, include=TRUE,echo=TRUE,warning=FALSE,message=FALSE,error=FALSE}
prop.table(table(df$y))
ggplot(df, aes(x=y, fill=y)) + geom_bar() + theme_minimal()
```

> Insight: The dataset is imbalanced, with only ~11.7% success rate.

## 2. Statistical Analysis (Chi-Square Test)
> Does the customer's job affect the subscription rate?

```{r 2, include=TRUE,echo=TRUE,warning=FALSE,message=FALSE,error=FALSE}
chisq.test(table(df$job, df$y))
```

> Insight: Since p-value < 0.05, the job category is a significant predictor of success.


## 3. Logistic Regression Results
> We built a model to predict the probability of subscription.

```{r 3, include=TRUE,echo=TRUE,warning=FALSE,message=FALSE,error=FALSE}
model <- glm(y ~ age + job + marital + balance + duration, data = df, family = binomial)
summary(model)
```

> Key Findings: Students and retirees have the highest probability of subscribing. Increased call duration also significantly boosts success odds.




